---
title:    "When Science Strikes Back"
subtitle: "Tables and Figures"
author:   "Gabriel Caser dos Passos and Nelson Ricardo Laverde Cubillos"
format:   pdf
editor:   visual
execute:
  echo: false
toc: true
---



```{r include = FALSE}
# TODOS

## Incluir titulo da tabela Sum Stats
## Melhorar tabela no código em .R colocando sublinhas 

# Running all scripts that generate figures and tables
source("code/00_main_code.R")
```


## Summary of Data Sources

| **Data Source**                                                                  | **Description**                                                            |
|-------------------------------------|-----------------------------------|
| Base dos Dados (Dahis et al., 2022) and Tribunal Superior Eleitoral (TSE)        | Information on mayors and elections.                                       |
| RAIS (Brazilian Ministry of Labor database)                                      | Occupation data.                                                           |
| SIVEPGripe                                                                       | Epidemiological outcomes data (hospitalizations, deaths).                  |
| 2010 Brazilian National Census                                                   | Demographic data.                                                          |
| IEPS Data Index                                                                  | Public health data.                                                        |
| Power and Rodrigues-Silveira (2019)                                              | Ideological measures.                                                      |
| De Souza Santos et al. (2021) and National Confederation of Municipalities (CNI) | Data on Non-Pharmaceutical Interventions (NPIs) between May and July 2020. |

: Summary of Data Sources

{{< pagebreak >}}

## Main Variables in the Study

| **Variable**                          | **Description**                                                                                    |
|------------------------|------------------------------------------------|
| Cases per 100k inhabitants            | Number of COVID-19 cases per 100,000 inhabitants, based on municipal data.                         |
| Hospitalizations per 100k inhabitants | Number of hospitalizations due to COVID-19 per 100,000 inhabitants.                                |
| Deaths per 100k inhabitants           | Number of deaths from COVID-19 per 100,000 inhabitants.                                            |
| STEM candidate                        | Indicator for whether a candidate has worked in STEM for at least 6 months or holds a STEM degree. |
| STEM occupation                       | Defined as per CBO classification list by Machado et al. (2021).                                   |
| STEM education                        | Based on data from Escavador, social media, and machine learning classification.                   |
| STEM winning margin                   | Vote margin between the first and second most-voted candidates, positive if a STEM candidate won.  |
| Cohort                                | List of candidates registered in the 2016 local executive elections.                               |
| Tenure                                | Employment time in a STEM occupation, calculated using RAIS data.                                  |

: Main Variables in the Study

## Summary Statistics

```{r}
# Carrega o arquivo da tabela como texto
texto <- readLines("outputs/tables/table_sum_stats.md")
# Renderiza o conteúdo como Markdown
knitr::asis_output(paste(texto, collapse = "\n"), meta = ":Tabela Teste")
```

: Summary Statistics

```{r}
dados_sumstats <- readRDS(paste(data_dir, "/final/", data, sep = ""))
nobs_sumstats  <- nrow(dados_sumstats)
cohorts_used   <- unique(dados_sumstats$coorte)
```


Notes: This table aggregates the summary statistics of all the observations used in the study (`r nobs_sumstats`). Municipalities chosen were those that held ordinary elections in selected years (`r cohorts_used`) whose mayor was elected in the first round and among the top two most voted was a STEM candidate and a Non-STEM one with college degree. NPI data has null values since not all the mayors responded to the survey.
